Ultrafast Electron Microscopes: Design Criteria, Electron Sources, and Column Modeling

### 2013-04-08 inc/photocathode/este/este.tex
fixed binning problem with este plot (and cleaned things up a bit while I was at it)

\begin{figure}
  \centering
  \input{fig3}
  \caption[Electron emission vs UV laser pulse energy for GaSb and InSb]{
    Number of electrons emitted per pulse as a function of the incident 261nm, UV laser pulse energy for GaSb (open squares) and InSb (filled circles): Linear efficiency dependences are shown by the solid lines.
    The laser pulse energy invariance of the Fourier plane electron beam size (HWe$^{-1}$M right axis; open squares) for GaSb and a representative raw Fourier plane beam image is also shown.
  }
  \label{fig:este-semicond}
\end{figure}

>>>>

\begin{figure}
  \centering
  \input{este_plot}
  \caption[Electron emission vs UV laser pulse energy for GaSb and InSb]{
    Number of electrons emitted per pulse as a function of the incident 261nm, UV laser pulse energy for GaSb (filled circles) and InSb (open circles): Linear efficiency dependences are shown by the solid lines.
    The laser pulse energy invariance of the HWe$^{-1}$M Fourier plane electron beam size (filled squares) for GaSb and a representative raw Fourier plane beam image is also shown.
  }
  \label{fig:este-semicond}
\end{figure}
